Adaptative neigbouring methods applied to telephonic base stations

### 2024-08-20 article.tex
Modification partie 5 (en cours)

Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
\section{Reminder on existing methods}
\subsection{Finding potential neighbours}
When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.

@@

\section{Contributions}
\noindent Each of the precedent methods gives us a list of potential neighbours for each \acrshort{bs}.
However, we know that some of this neighbouring connexions are wrong,
either because of the neighboring graph construction method or physical specificities linked to the base stations themselves.

Thus, we need to find methods to detetect and erase these bad connexions.

The main innovation of our work compared to this one \cite{art_del_paq} is to take in account the difference of \acrshort{bs}'s density.

@@

\subsubsection{\acrshort{dbscan}}
The goal here is to separate points that seem to belong to a denser conglomerate of base station, from the others who are a bit more spaced
to cover the countryside.

That is called density based clustering. The main method to do that is \acrshort{dbscan}.

It consists in detecting clusters based on the density, using two parameters:

\begin{itemize}
    \item \emph{$\varepsilon$}: A distance threshold under which two points are considered close enough to be considered neighbours;   
    \item \emph{$n_{\text{min}}$}: The shortest number of neigbours a points needs to have to be considered as a core point of a cluster.
\end{itemize}

Despite the efficiency of this method, it is not the best adapted to our problem because it's only giving us if a \acrshort{bs} is considered 
in a city or not, it doesn't split the points that are in a city into the four categories presented above.

\subsubsection{\acrshort{hdbscan}}
This method, introduced here \cite{10.1007/978-3-642-37456-2_14} is a variation of the \acrshort{dbscan} method. It consists
in selecting the best clusters after testing their persistence by making the $\varepsilon$ parameter vary. It's main particularity
is that it allows to detect clusters of different densities.

To each point who belong to a cluster is associated a probability that symbolises the degree of certainty for this point to belong
to the said cluster.

This probability can be used to separate the center of the city (where the probability is very high) from the rest of the city. However,
it cannot be precise enough to separate the clusters into the four categories.

@@

\subsection{Filtering criteria}

>>>>

Finally, in order to simplify viewing, we will apply our neighbouring only on the Normandie region just because this is where we live.
\section{Reminder on existing methods\label{sec:reminder}}
\subsection{Finding potential neighbours}
When we are looking for neighbours, we need, at first, a list of potential neighbours for each point.
For that, we will construct a neigbouring graph $G = (P, U)$ where $P$ is the set of all points and each edge in $U$ represents a neighbouring relation.

@@

\section{Contributions}
\noindent In section~\ref{sec:reminder}, we have seen that we can find the neighbours of base stations
by combining a potential neighbouring graph and filtration criteria. This methodology gives pretty good results \cite{art_del_paq}.

However, in certain cases like in a city, the filtration criteria aren't precise enough. We, therefore, need to find some ways to measure base stations' density.

@@

\subsubsection{\acrshort{dbscan}}
DBScan gives only two categories : city - countryside
[permet de faire que 2 categories : pas assez précis (mais ptet à mettre dans résultats)]

\subsubsection{\acrshort{hdbscan}}
...

@@

\subsection{Improvement of filtering criteria}
